### 2021-04-15 input/abstract.tex
abstract pass 1

\begin{abstract}
  %% Context and problem
  Edge infrastructures constitute an alternative to Cloud Computing
  that aims at improving on latency and traffic by providing computing
  and storage capabilities closer to data producers and consumers.
  %% Edge infrastructures have been proposed as an alternative to Cloud
  %% Computing to provide computing and storage capabilities closer to
  %% the locations where data is generated/consumed, with the objectives
  %% of reducing the latency and the volume of data passing through the
  %% network.
  A few systems, such as content delivery networks, replicate and
  distribute produced data in these infrastructures.
  % A few systems have been proposed to store data in those
  % infrastructures.
  Locating the closest replica of a specific content requires to
  maintain an up-to-date index of all live replicas along with their
  respective locations. 
  %
  Unfortunately, relying on a centralized service would bring
  scalability issues, single point of failure, as well as additional
  middleman latency where locating replicas may effectively take more
  time than actually downloading contents. Instead, data consumer
  \processes must maintain an up-to-date index
  themselves. Unfortunately, maintaining an index of all live replicas
  at every \process would prove overly costly in terms of memory and
  generated traffic, especially in large scale dynamic systems where
  \processes create and destroy replicas at any time.
  % while flooding approaches will not enable the maintenance of such
  % an index for each node in large systems, relying on a dedicated
  % service contradicts with the properties of Edge infrastructures in
  % terms of locality and robustness

>>>>

\begin{abstract}
  %% Context and problem
  %By providing computing and storage capabilities closer to data
  %producers and consumers, Edge infrastructures constitute an alternative to Cloud Computing platforms
  %A few systems have been proposed to store and manipulate data in
  %Edge infrastructures. By relying for instance on appropriate
  %replication policies, those systems reduce the impact of the latency
  %as well as the volume of data passing through the network overall.
  %
  Although, there is no major solution to store and manipulate data in
  Edge infrastructures yet, existing proposals demonstrated the relevance of appropriate
  replication strategies to bring contents closer to consumers, reducing the impact of the latency as
  well as the volume of data passing through the network overall.
%
  Unfortunately, locating the closest replica of a specific content requires to
  maintain an up-to-date index of all live replicas along with their
  respective locations.
  %
  %Current proposals built on a centralized service face scalability
  %issues, single point of failure, as well as latency penalities where
  %locating replicas may effectively take more time than actually
  %downloading contents. Instead, data consumer \processes must
  %maintain an up-to-date index themselves. Unfortunately, maintaining
  %an index of all live replicas at every \process would prove overly
  %costly in terms of memory and generated traffic, especially in large
  %scale dynamic systems where \processes create and destroy replicas
  %at any time.
  % 
  Relying on a remote service contradicts with the properties of
  Edge infrastructures as locating replicas may
  effectively take more time than actually downloading contents.
  At the opposite,  maintaining such an index at every \process would prove overly
  costly in terms of memory and generated traffic, especially in an
  edge context where \processes create and destroy replicas at any
  time.
  % while flooding approaches will not enable the maintenance of such
  % an index for each node in large systems,
